Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Please, use of 'they' is always preferable than 'he/she'

WSO2 Enterprise Mobility Manager (WSO2 EMM) \cite{WSO2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:
% Antonio - cambio esto porque las negritas no se suelen usar apenas y para mantener la concordancia en formato con el resto de listas
\begin{itemize}
  \item \textit{Mobile Device Management}: Which is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment. It should be noted that this tool allows tracking every enrolled device, as well as obtaining reports and analytics of their use.
  \item \textit{Mobile Application Management}: With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
  \item \textit{Enterprise App Store}: This store provides users with both enterprise and public applications approved by the company.
  \item \textit{Mobile Data Security}: WSO2 also allows the user's data to be encrypted via password.
\end{itemize}

@@

Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface he/she can interact with. Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful. The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.

@@

\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback. The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''. 
% Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.

>>>>

WSO2 Enterprise Mobility Manager (WSO2 EMM) \cite{WSO2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:
% Antonio - cambio esto porque las negritas no se suelen usar apenas y para mantener la concordancia en formato con el resto de listas
\begin{itemize}
  \item \textit{Mobile Device Management}: It is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment. It should be noted that this tool allows tracking every enrolled device, as well as obtaining reports and analytics of their use.
  \item \textit{Mobile Application Management}: With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
  \item \textit{Enterprise App Store}: This store provides users with both enterprise and public applications approved by the company.
  \item \textit{Mobile Data Security}: WSO2 also allows the user's data to be encrypted via password.
\end{itemize}

@@

Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with. Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful. The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.

@@

\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback. The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''-type. 
% Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
% Paloma -  "forward slash" no significa guión. Un forward slash es un / que sí había muchos en el texto.
All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.
